Probability

### 2016-04-08 prob.tex
prob.tex "Example 6. [Quantum probability measure]" update, but bibtex cannot work in TeXclipse so far...

\begin{example}[Quantum probability measure]
Like in the classical case, there are $2^8$ events. But as Mermin
explains in a simple example (Quantum Mysteries Revisited), here is a
possible probability measure: 
\[\begin{array}{rcl}
\mathbb{P}(S) &=& \left.\{ \begin{array}{ll}
  1/8 & \mbox{if there is an odd number of $L$} \\
  \ldots
  \end{array}\right.
\end{array}\]
Interestingly and paradoxically, it is \emph{not} possible to analyze
each electron independently and assign a consistent probability to
each one locally and non-contextually. 
\end{example}

@@

>>>>

\begin{example}{[}Quantum probability measure{]} Like in the classical
case, there are $2^{8}$ events. But as Mermin explains in a simple
example~\cite{MerminPRL1990}, here is a possible probability measure:
\[
\begin{array}{rcl}
\mathbb{P}(\{LLL\}) & = & \frac{1}{4}\\
\mathbb{P}(\{LLR\}) & = & 0\\
\mathbb{P}(\{LRL\}) & = & 0\\
\mathbb{P}(\{LRR\}) & = & \frac{1}{4}\\
\mathbb{P}(\{RLL\}) & = & 0\\
\mathbb{P}(\{RLR\}) & = & \frac{1}{4}\\
\mathbb{P}(\{RRL\}) & = & \frac{1}{4}\\
\mathbb{P}(\{RRR\}) & = & 0\\
\mathbb{P}(E) & = & \sum_{\omega\in E}\mathbb{P}(\left\{ \omega\right\} )
\end{array}
\]
In contrast with the classical example previously, the probability
of each electron is not independent~\cite{GrahamKnuthPatashnik1994,inun.425605319950101,rohatgi2011introduction},
i.e., we cannot find three probability space for each subsystem such
that 
\[
\mathbb{P}(\{abc\})=\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
\]
Correlated variables are also common in the classical world. For example,
if the first coin is head or tail decided by whether the temperature
is higher than a particular degree and the second coin is decided
by whether Coca Cola is sold more than a particular amount, then we
know these two coins are correlated. Einstein, Podolsky, and Rosen~\cite{EPR1935}
suggested any correlated quantum probability results may be interpreted
classically. For example, maybe the natural actually rolls an tetrahedron
die with $\{LLL,LRR,RLR,RRL\}$ in its four faces, and this tetrahedron
die could not be accessed by human for some reasons so that we think
we are handling three electrons.

The interesting part is that three electrons cannot be measured the
spin only along the $x$ axis, but also along the $y$ axis with the
result down ($D$) or up ($U$).

Interestingly and paradoxically, it is \emph{not} possible to analyze
each electron independently and assign a consistent probability to
each one locally and non-contextually. 
\end{example}

@@

\bibliographystyle{plain}
\bibliography{discreteGBKS}
